StackTokens: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-03 fully-abstract-comp/popl2019/paper.tex
Fix citations.

Capability machines originate with Dennis and Van Horn~\cite{Dennis:1966:PSM:365230.365252} and we refer to Levy~\cite{Levy1984capability} and Watson et al.~\cite{Watson2015Cheri} for an overview of previous work.
The capability machine formalized in \sectionname~\ref{sec:capab-mach-with} is modeled CHERI~\cite{Watson2015Cheri,Woodruff:2014:CCM:2665671.2665740}.
The latter is a recent and relatively mature capability machine, which combines capabilities with a virtual memory approach, in the interest of backwards compatibility and gradual adoption.
In the interest of simplicity, we have omitted features of CHERI that were not needed for modelling StackTokens (e.g.\ local capabilities, virtual memory).

@@

More closely related to our work are papers that use separate per-component stacks, a trusted stack manager and some form of memory isolation to enforce control-flow correctness as part of a secure compilation result~\citep{patrignani_modular_2016-1,juglaret_beyond_2016-1}.
Our work differs from theirs in that we use a different low-level security primitive (a capability machine with local capabilities rather than a machine with a primitive notion of compartments) and we do not use per-component stacks or a trusted stack manager, but a single shared stack and a decentralized calling convention based on linear capabilities.
Both prove a secure compilation result from a high-level language, which clearly implies a general form of control-flow correctness, but that result is not separated from the results about other aspects of their compiler.

@@

The fact that our full abstraction result only applies to reasonable components (see Section~\ref{sec:form-secur-with}) makes it related to full abstraction results for unsafe languages.
In their study of compartmentalization primitives, \Cite{juglaret_beyond_2016} discuss the property of Secure Compartmentalizing Compilation (SCC): a variant of full abstraction that is able to deal with source languages with undefined behavior (together with other benefits).
Essentially, they modify standard full abstraction so that preservation and reflection of contextual equivalence are only guaranteed for components that are {\itshape fully defined}, which means essentially that they do not exhibit undefined behavior in any fully defined context.
In follow-up work, they extend this approach to apply in scenario's where components only exhibit undefined behavior after a number of well-defined steps~\citep{DBLP:journals/corr/abs-1802-00588}.
If we see reasonable behavior as defined behavior, then our full abstraction result can be seen as an application of this same idea.

>>>>

Capability machines originate with \citet{dennis_programming_1966} and we refer to \citet{levy_capability-based_1984} and \citet{watson_cheri:_2015} for an overview of previous work.
The capability machine formalized in \sectionname~\ref{sec:capab-mach-with} is modeled CHERI~\cite{watson_cheri:_2015,woodruff_cheri_2014}.
The latter is a recent and relatively mature capability machine, which combines capabilities with a virtual memory approach, in the interest of backwards compatibility and gradual adoption.
In the interest of simplicity, we have omitted features of CHERI that were not needed for modelling StackTokens (e.g.\ local capabilities, virtual memory).

@@

More closely related to our work are papers that use separate per-component stacks, a trusted stack manager and some form of memory isolation to enforce control-flow correctness as part of a secure compilation result~\citep{patrignani_modular_2016,juglaret_beyond_2016}.
Our work differs from theirs in that we use a different low-level security primitive (a capability machine with local capabilities rather than a machine with a primitive notion of compartments) and we do not use per-component stacks or a trusted stack manager, but a single shared stack and a decentralized calling convention based on linear capabilities.
Both prove a secure compilation result from a high-level language, which clearly implies a general form of control-flow correctness, but that result is not separated from the results about other aspects of their compiler.

@@

The fact that our full abstraction result only applies to reasonable components (see Section~\ref{sec:form-secur-with}) makes it related to full abstraction results for unsafe languages.
In their study of compartmentalization primitives, \Citet{juglaret_beyond_2016} discuss the property of Secure Compartmentalizing Compilation (SCC): a variant of full abstraction that is able to deal with source languages with undefined behavior (together with other benefits).
Essentially, they modify standard full abstraction so that preservation and reflection of contextual equivalence are only guaranteed for components that are {\itshape fully defined}, which means essentially that they do not exhibit undefined behavior in any fully defined context.
In follow-up work, they extend this approach to apply in scenario's where components only exhibit undefined behavior after a number of well-defined steps~\citep{DBLP:journals/corr/abs-1802-00588}.
If we see reasonable behavior as defined behavior, then our full abstraction result can be seen as an application of this same idea.
